Supplementary Material for Asymmetry paper

### 2020-05-11 Supplementary/Sup_mat.Rmd
How to add figure captions

---
title: "Supplementary Material for Asymmetry paper"
output: 
  bookdown::pdf_document2:
    fig_caption: false
---

@@

We started by fitting a a beta distribution to the _Throwing Experiment_ data from Clarke and Hunt (2016) using the `fitdistrplus` package. We then investigated how well we could detect various effects, and how this varied based on the sample size.

@@

```{r load data and draw distributions, include = T, echo = F, fig.height = 3}
load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")

>>>>

---
title: "Supplementary Material for Asymmetry paper"
output: 
  bookdown::pdf_document2
---

@@

```{r loaddata, include = T, echo = F, fig.height = 3, fig.cap="Warren write some text."}
load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")
```

We started by fitting a a beta distribution to the _Throwing Experiment_ data from Clarke and Hunt (2016) using the `fitdistrplus` package. We then investigated how well we could detect various effects, and how this varied based on the sample size. See Figure 1a.

@@

```{r drawdistributions, include = T, echo = F, fig.height = 3, fig.cap="Warren write some text."}
load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")
